%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e]{altacv}
\usepackage{hyperref}
\PassOptionsToPackage{dvipsnames}{xcolor}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=1.25cm,right=9.5cm,marginparwidth=7.75cm,marginparsep=1.0cm,top=1.15cm,bottom=1.25cm}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{gray}{0.005}
\definecolor{LightGrey}{gray}{0.2}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}


% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Sarthak Jain}
\tagline{Experiences in Development, Testing and Marketing}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
% \photo{3.3cm}{profile.jpg}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  
    \email{\color{blue} \href{mailto:sarthak.jain2404@gmail.com?Subject=Regarding Resume}{\small sarthak\Large.\small jain2404@gmail.com}}
    \phone{\color{blue}\href{tel:+917011189445}{\small +91 7011189445}}
%  \mailaddress{Address, Street, 00000 County}
%    \location{\color{blue}\href{https://www.google.com/maps/place/Delhi%/}{\small New Delhi}}
%  \homepage{marissamayr.tumblr.com/}
  \twitter{\color{blue}\href{https://twitter.com/sarcastic_sark/}{\small {@sarcastic\_sark}}}
    \linkedin{\color{blue}\href{https://www.linkedin.com/in/sarthak-jain24apr98/}{\small sarthak-jain24apr98}}
    \github{\color{blue}\href{https://github.com/sarthak-1998}{\small sarthak-1998}} % I'm just making this up though.
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[SideBar]{Professional Experience}

\cvevent{\href{https://codingblocks.com/team.html}{Product Manager Intern}}{\color{blue}\href{https://codingblocks.com}{Coding Blocks}}{Nov2018-Ongoing}{Delhi, India}
\begin{itemize}
\item Spearheaded the adoption of new methodologies in company to bring in real-time data monitoring, trace-ability and achieve compliance. 
\item Consistently tested CB Online App and website for bugs.
\item Researched and pursued new business campaigns for the growth of the business resulted in 1500 times increase in user sign-ups.
\item Introduced seamless integration of Tech and it's Marketing by forming bridge of workflow.

\end{itemize}

\cvevent{Web Developer Intern}{\color{blue}\href{https://allindiaradio.gov.in/}{All India Radio (AIR), Prasar Bharati}}{June2018-July2018 }{New Delhi, India}
\begin{itemize}
\item Maintained and Created a wonderful website to digitizes the Complaint filing System for the Government quarter residents. 
\item Constantly updated and Monitored the company’s database systems.

\end{itemize}


\cvevent{Social Media Manager}{\color{blue}\href{https://www.shopnani.com/}{ ShopNani }}{Dec2016-Jan2017 }{New Delhi, India}

\begin{itemize}
\item Wrote niche articles on latest prevailing Tech news for the website, Blog and social media accounts for daily postings.
Evaluated different insights and Demographics. Handled the company’s online presence.
 \item Monitored ongoing marketing campaigns
Increased social media following and clicks by 200\%

\end{itemize}



\cvsection{ Achievements and Talks}

\begin{itemize}
     \item  \color{LightGrey} Selected for the \color{blue}\href{https://drive.google.com/drive/folders/1W8HZmATotqPVJcRV8dol9LuKinMlSWxu?usp=sharing }{Top 50 Marketing \& Advertising Leaders Award} \color{LightGrey} by MADCon 2019.
    \item  \color{LightGrey} Speaker at \color{blue}G\color{red}o\color{yellow}o\color{blue}g\color{teal}l\color{red}e \color{LightGrey} I/O Extended 2019. 
    \item  \color{LightGrey} Speaker at \color{LightGrey} GDG DevFest Punjab 2019.
     %\item Lead multiple campaigns to drive more users on platform and increase conversions significantly.
  \item Speaker at Nit Kurukshetra, LPU, Manipal University Jaipur, Delhi University etc. Educated and activated over 600 students on professional growth in IT Industry.  
    
    \end{itemize}

\cvsection{ Education}
\cvevent{\small{B.Tech - Computer Science }}
{\small{Maharaja Agrasen Institute of Technology}}
{ Jun 2016 -- May 2020 \hspace{1cm} CGPA: 7.43 }{}
\cvevent{\small{Senior Secondary Education- 12th (CBSE)}}{\small{Kendriya Vidyalaya sector-8 Rohini, Delhi}}{2016 \hspace{1cm} Percentage: 90.2}{} 
\cvevent{\small{Secondary Education-10th (CBSE)}}{\small{Kendriya Vidyalaya sector-8 Rohini, Delhi}}{
2014 \hspace{1cm} CGPA: 10}{}




%% If the NEXT page doesn't start with a \cvsection but you'd
%% still like to add a sidebar, then use this command on THIS
%% page to add it. The optional argument lets you pull up the
%% sidebar a bit so that it looks aligned with the top of the
%% main column.
% \addnextpagesidebar[-1ex]{page3sidebar}


\end{document}
