
\cvsection{ Projects}
\cvproject{\color{blue}\href{https://sarthakj.me}{ sarthakj.me - \color{black}Node.js}}
\begin{itemize}
\item My Website hosted on AWS with multiple features.
\end{itemize}


\cvproject{\color{blue}\href{https://github.com/sarthak-1998/Rap-Generator}{Lyrics Generator - \color{black}Python}}
\begin{itemize}
\item A Markov Chain based model to generate lyrics of a song. 
\end{itemize}

\cvproject{\color{blue}\href{https://github.com/sarthak-1998/Parking-Lot-Problem}{Parking Lot App - \color{black}Ruby}}
\begin{itemize}
\item Parking lot terminal based application for effective parking solutions.
\end{itemize}

\cvproject{\color{blue}\href{https://github.com/sarthak-1998/codingblocks.com}{Coding Blocks Main Website - \color{black}Vanilla JavaScript}}
\begin{itemize}
\item The Coding Blocks main website.
\end{itemize}

\cvproject{\color{blue}\href{https://github.com/sarthak-1998/shortlr2-backend}{Short Link Generator - \color{black}Node.js}}
\begin{itemize}
\item Source code for back-end of Short link generator with additional features such as UTM tracking.
\end{itemize}

\cvproject{\color{blue}\href{https://github.com/sarthak-1998/LIVE-Code-Share}{Live Code Share - \color{black}Node.JS}}
\begin{itemize}
\item Web app to support Live Code sharing \& chatting feature.
\end{itemize}


\cvproject{\color{blue}\href{https://github.com/sarthak-1998/RWA-WebApp-AIR}{Web App for AIR - \color{black}C\# and ASP.Net}}
\begin{itemize}
\item This is the logistic application developed to digitize the manual filing of complaints and their status tracking for Government quarters.
\end{itemize}

\cvsection{\Large Skills}
C++, C\#, JavaScript, Python 3, MySQL \newline

    
    \cvsection{\large Extra Curriculum}
    
    \cvevent{\textbf{\small{\color{blue}\href{https://cse.mait.ac.in/index.php?option=com_content&view=article&id=546}{TechCom (Coding society of MAIT)}}}}{{\small Vice-President}}{\small 2019 -- Present}{\small New Delhi,India}


    \cvevent{\textbf{\small{\color{blue}{Campus Blocks (Student Chapter ) }}}}{{\small Chief Operating officer}}{\small 2019 -- Present}{\small New Delhi,India}

\cvevent{\textbf{\small{\color{blue}\href{https://www.facebook.com/codematrixsociety}{CODEMATRIX (Technical society)}}}}{{\small Marketing and Public Relations Manager}}{\small 2018 -- Present}{\small New Delhi,India}

   \cvsection{ \large   Technical Forums} 

\begin{itemize}
\item Beta Testing mobile ROMs for Lenovo ZUK Z1 and OnePlus 5T.
\item Active member of XDA forum and OnePlus community (Level 8)
\item Beta Testing plethora of Android apps.

\end{itemize}
    
    
\divider

\textbf{\textit
{\underline{Note:If you’re viewing a soft copy, all \color{blue} blue texts}
\underline{are \colorbox{VividPurple}{ \color {white} {hyperlinks}}, you can click to view details}}}.
